MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-26 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
used Lucas's code to get greek letters to show up in the heatmaps!

ggplot(merge24And3, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  labs( y = "Assay")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

>>>>

ggplot(merge24And3, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  scale_y_discrete(breaks = merge24And3$altAssayNames,labels =merge24And3$altAssayNames)+
  labs( y = "Assay")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

### 2016-09-26 MSD_panels_1_2_3_explant_sup_analysis.Rmd
used Lucas's code to get greek letters to show up in the heatmaps!

ggplot(mergeMock, aes(x = Timepoint, y = logMockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  #geom_hline(yintercept = 0)+
  ggtitle("Mock Subtracted Analyte Concentrations")

@@

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

@@

ggplot(merge24And3, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  labs( y = "Assay")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")

>>>>

ggplot(mergeMock, aes(x = Timepoint, y = logMockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Mock Subtracted Analyte Concentrations")

@@

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  scale_y_discrete(breaks = merge24And3$Assay,labels =merge24And3$Assay)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

@@

ggplot(merge24And3, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  labs( y = "Assay")+
  scale_y_discrete(breaks = merge24And3$altAssayNames,labels =merge24And3$altAssayNames)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
